Community Detection Methods for Generalized Random Dot Product Graphs

### 2021-06-02 proposal/slides.Rmd
minor tweaks

* $P_{ij} = \theta$
* Not a block model

@@

**Theorem** (KTT): 
Let $\hat{B}_n$ with entries $\hat{B}_n^{(ij)}$ be the affinity matrix from OSC. 
Then $\forall$ pairs $(i, j)$ belonging to different communities 
and sparsity factor satisfying $n \rho_n = \omega\{(\log n)^{4c}\}$,

@@

Examples:

1. $r = 1$ and each $\gamma_k$ is a point mass $\implies$ SBM
2. $r = 1$ and the range of each $\gamma_k$ is a segment from the origin to point $y_k$ with $\|y_k\| \leq 1$ $\implies$ DCBM
3. $r = K$ and the range of each $\gamma_k$ is the hyperplane of coordinates $x_{K (k-1) + 1}$ to $x_{k K}$ $\implies$ PABM

>>>>

* $P_{ij} = \theta$ (not a block model)
* 1 parameter $\theta$

@@

**Theorem** (KTT): 
Let $\hat{B}_n$ with entries $\hat{B}_n^{(ij)}$ be the affinity matrix from OSC. 
Then $\forall$ pairs $(i, j)$ belonging to different communities 
and sparsity factor satisfying $n \rho_n = \omega\big((\log n)^{4c}\big)$,

@@
